Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-05 measurements.tex
Use the ideal plots

\subsubsection{Encoding}
Figs. \ref{fig:}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf2.pdf}
        \caption[]%
        {{\small Goodput vs. Generation size for $GF(2)$}}    
        \label{fig:mean and std of net14}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}  
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf256.pdf}
        \caption[]%
        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
        \label{fig:mean and std of net24}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf2.pdf}
        \caption[]%
        {{\small Goodput vs. Packet size for $GF(2)$}}    
        \label{fig:mean and std of net34}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf256.pdf}
        \caption[]%
        {{\small Goodput vs. Packet size for $GF(2^8)$}}    
        \label{fig:mean and std of net44}
    \end{subfigure}
    \caption[]
    {\small Encoder goodput measurements for the \ac{Raspi} 1} 
    \label{fig:enc_good_rasp1}
\end{figure*}

>>>>

\subsubsection{Encoding}

Fig. \ref{fig:enc_good_rasp1} shows the results of the encoder goodput measurements
for the \ac{Raspi} 1.

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_encoder_Binary_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $GF(2)$}}    
        \label{fig:enc_good_rasp1_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}  
        \centering 
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_encoder_Binary8_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
        \label{fig:enc_good_rasp1_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_encoder_Binary_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $GF(2)$}}    
        \label{fig:enc_good_rasp1_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_encoder_Binary8_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $GF(2^8)$}}    
        \label{fig:enc_good_rasp1_packet_gf2}
    \end{subfigure}
    \caption[]
    {\small Encoder goodput measurements for the \ac{Raspi} 1} 
    \label{fig:enc_good_rasp1}
\end{figure*}
